### 2021-06-04 README.Rmd
Add README GitHub Action

By default, both functions include an "Overall" risk of bias domain. To prevent this, set `overall = FALSE`.

```{r, eval=FALSE}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", overall = FALSE)
summary_rob
```

``` {r, echo = FALSE}
plot <- rob_summary(data = data_rob2, tool = "ROB2", overall = FALSE)
file = paste0("man/figures/robplot",fig_count,".png")
rob_save(plot, file)
fig_count <- fig_count + 1
```
<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>

```{r, eval=FALSE}
rob_traffic_light(data = data_rob2,
                  tool = "ROB2",
                  overall = FALSE)
```

``` {r, echo = FALSE}
plot <- rob_traffic_light(data = data_rob2,
                                      tool = "ROB2",
                                      overall = FALSE)
file = paste0("man/figures/robplot",fig_count,".png")
rob_save(plot, file)
fig_count <- fig_count + 1
```
<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>

>>>>

By default, both functions include an "Overall" risk of bias domain. To prevent this, remove the overall column from your dataset and set `overall = FALSE`.

```{r, eval=FALSE}
summary_rob <- rob_summary(data = data_rob2[1:6], tool = "ROB2", overall = FALSE)
summary_rob
```

``` {r, echo = FALSE}
plot <- rob_summary(data = data_rob2[1:6], tool = "ROB2", overall = FALSE)
file = paste0("man/figures/robplot",fig_count,".png")
rob_save(plot, file)
fig_count <- fig_count + 1
```
<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>

```{r, eval=FALSE}
rob_traffic_light(data = data_rob2[1:6],
                  tool = "ROB2",
                  overall = FALSE)
```

``` {r, echo = FALSE}
plot <- rob_traffic_light(data = data_rob2[1:6],
                                      tool = "ROB2",
                                      overall = FALSE)
file = paste0("man/figures/robplot",fig_count,".png")
rob_save(plot, file)
fig_count <- fig_count + 1
```
<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>
